---
title: "Cabbages"
author: "Thelma"
date: "5/31/2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
# Methods
$H_O$:: there is no difference in average vit c between c39 and c52 cultivation methods

# Method
we are explaining the numerical variable of vitamin C by examining the categorical variable cultivation we will use the T test to compare the mean of the vitamin c groups from the vit c


<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
boxplot(VitC~Cult,data=veggy)
```


the category c39 for cultivating had an overall lower means for the numerical results of the vit c while the
c52 category had a higher mean of the vit c when using their cultivation method  



<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

the cultivation 39 had a median of s1.0,while c52 had a median of 64.5 c39 had a mean of 51.0 meaning the cultivation method was successful  

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

based on our two sample T test we can infer that the p value is 0.00000003405 from this we can reject the null hypothesis because the probability of the sample result was very unlikely meaning the null hypothesis is rejected


# Discussion and Conclusion
e
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
the difference between the two categories we had, cultivation methods c 39 and c52 were found to have a numerical difference of the vit c produced in the cabbages made rejected the null hypothesis after seeing the results of the T rest. the c39 had a means of s1.5 while the c52 gorup had a mean of 64.5 or p value of this this test was 0.0000003405  